04_DESeq_sexes

### 2019-05-25 analysis/04_DESeq2_sexes.Rmd
now with all pca violoin plots

```{r returntotalDEGs, eval = T}
#DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
#DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
#DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGss.male_pituitary <- returntotalDEGs(dds.male_pituitary)
#DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)
```

```{r plotDEGs, eval = T}
#a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
#c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
#d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGss.male_pituitary, "male pituitary")
#f <- plottotalDEGs(DEGs.male_gondad, "male gonad")
```

@@

```{r pcadf, eval=F}
p1 <- plotPCAs(dds.female_hypothalamus, "female hypothalamus")
p2 <- plotPCAs(dds.female_pituitary, "female pituitary")      
p3 <- plotPCAs(dds.female_gonad, "female gonad")
p4 <- plotPCAs(dds.male_hypothalamus, "male hypothalamus")
p5 <- plotPCAs(dds.male_pituitary, "male pituitary")
p6 <- plotPCAs(dds.male_gondad, "male gonad")
p1
p2
p3
p4
p5
p6

```

```{r pca, fig.dim = c(12, 10), eval=F}
mylegend <- get_legend(p1)

theme_noaxislabels <- theme(legend.position = "none", axis.title.x=element_blank(),axis.text.x=element_blank())

allPC1s <- plot_grid(p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels),
                     nrow = 3, rel_heights = c(0.3, 0.3, 0.4))

pc1 <- plot_grid(mylegend, allPC1s, nrow = 2, rel_heights = c(0.15, 1.0))
pc1

>>>>

```{r returntotalDEGs, eval = F}
DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGs.male_pituitary <- returntotalDEGs(dds.male_pituitary)
DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)
```

```{r plotDEGs, eval = T}
#a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
#c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
#d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary")
#f <- plottotalDEGs(DEGs.male_gondad, "male gonad")
```

@@

```{r returnPCAs, eval=T}
pcas.female_hypothalamus <- returnPCAs(dds.female_hypothalamus)
pcas.female_pituitary <- returnPCAs(dds.female_pituitary)      
pcas.female_gonad <- returnPCAs(dds.female_gonad)
pcas.male_hypothalamus <- returnPCAs(dds.male_hypothalamus)
pcas.male_pituitary <- returnPCAs(dds.male_pituitary)
pcas.male_gondad <- returnPCAs(dds.male_gondad)
```

```{r plotpca, fig.dim = c(12, 10), eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels
```
```{r temp, eval = F}
mylegend <- get_legend(p1)

allPC1s <- plot_grid(p1 + theme_noaxislabels, 
                     p2 + theme_noaxislabels, 
                     p3 + theme_noaxislabels,
                     p4 + theme_noaxislabels,
                     p5 + theme_noaxislabels,
                     p6 + theme_noaxislabels,
                     nrow = 3, rel_heights = c(0.3, 0.3, 0.4))

pc1 <- plot_grid(allPC1s,mylegend,  nrow = 2, rel_heights = c(1.0, 0.15))
pc1
